\Huge Conferences in an Era of Expensive Carbon

### 2019-06-19 main.tex
Done with my pass

Most recently, we have been investigating how to purchase \emph{carbon
  offsets} to defray CO2e costs.
%
A carbon offset is sold by a vendor who uses the raised funds to
finance an activity that permanently avoids emitting an amount of
greenhouse gases. That the CO2e emission avoidance is truth and not
appearance can be certified by a watchdog organization. Typically,
planting trees is not a certifiable activity (since it's hard to
guarantee the trees won't be cut down), but installing methane capture
devices on landfill sites or buying fuel-efficient stoves to replace
open-fire cooking in poor communities can be.

Many organizations (including companies such as Google, Dell,
Microsoft, General Motors, Delta Airlines, Lyft, and Expedia, numerous
universities, and a number of academic societies) now buy carbon
offsets in order to reduce their overall footprint. ACM conferences
could do the same, and the purchases would be included in their public
accounting. We have been investigating this possibility for the past
year. ACM has now agreed that conference attendees can opt to purchase
an offset during registration, and ACM will use the designated funds
to purchase an offset. Even getting to this stage required some
investigation of the legality of ACM making the purchase on behalf of
the registrant~\cite{CarbonOFfsetReport}. Ideally, the purchase of
offsets would be made even simpler, but doing so requires further
thought.

@@

Publicly accounting for CO2e expenditures will incentivize some CO2e
reductions, but probably not major changes to conference system
itself, since doing so may negatively impact the value that
conferences provide.
%
Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that could
harm the scientific benefits they have all regularly experienced.
%
Nevertheless, it seems clear that the status quo is unsustainable, so
hard choices will have to be made. How to motivate organizers to make
them?

@@

What should ACM do with the funds collected from this surcharge?  One can
imagine many good uses, including buying carbon
offsets~\cite{CarbonOFfsetReport}, supporting ``green'' computing
research\bcp{can we mention some specifics?}, and defraying the costs of
virtualizing conferences (livestreaming, etc.).

(Mike: Here we can talk about data analysis, and how it could provide
help with this. We've started, and see that the situation is not very
clear. Describe some of our data.  Show the two diagrams.  Draw some
conclusions / discuss why it's hard to draw conclusions.

@@

The climate crisis is too important to ignore and too urgent to leave to
world leaders, to address at their own pace: rather, organizations at every
scale must confront their own contributions, raise awareness among their
members, and begin establishing new ways of doing business in the
lower-carbon future that is coming.  ACM should lead the way!

>>>>

Another simple, short-term expedient for lowering net the emissions
footprint of conferences is purchasing \emph{carbon
  offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this CO2e emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided to allow conferences to allow attendees to pay for an offset during
registration; the conference then uses the designated funds to purchase the
offset from a qualified vendor.  Some conferences are also experimenting
with corporate sponsorship of bulk offsets for the whole conference.  (It
should be noted that carbon offsets are a controversial tool.  Besides
issues with verifiability and permanence, some observers worry
that---especially given their currently quite low cost---they will encourage
complacency, leading organizations to postpone making the difficult changes
that will certainly be required to fully decarbonize society.  We agree that
offsets are at best a short-term measure, to be considered in parallel with,
not instead of, more difficult cutting.)

Beyond encouraging conferences to take these sorts of simple steps, public
accounting of conference emissions footprints will generate valuable data
that future organizers can use to optimize their own footprints.
%
\bcp{Talk about the little bit of data gathering that we've done.  Make the
  point that, if the public accounting of conference carbon footprints is
  detailed enough (e.g., including an origin city for each participant,
  rather than just aggregate statistics on average per-participant
  footprint), and if it's publicized in a centralized place and in a uniform
  format, then it becomes a resource for all sorts of useful analysis.}

@@

However, while publicly accounting for CO2e expenditures will incentivize
some CO2e reductions, it will probably not, by itself, induce major changes
to the conference system.  There are good reasons for this, since such
changes will undoubtedly impact the value that conferences provide.
%
Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that could
harm the scientific benefits they have all regularly experienced.

Indeed, a preliminary analysis that we have done with registration data for
recent SIGPLAN conferences raises as many questions as it answers.
\bcp{Talk about our data analysis, and how it could provide help with
  this. We've started, and see that the situation is not very
  clear. Describe some of our data.  Show the two diagrams.  Draw some
  conclusions / discuss why it's hard to draw conclusions.  (This would be a
  good place to refer to~\cite{ClimateCommitteReport}---we can enumerate
  some of the alternatives that one might have hoped the data would help us
  choose between.)}

\bcp{Tricky transition here.  I think the point we want to make is that
  these decisions are genuinely hard and painful, which is exactly what our
  data shows.}

Nevertheless, it seems clear that the status quo is unsustainable, so hard
choices will have to be made. How do we motivate organizers to make them?

@@

What should ACM do with the funds collected from this surcharge?  One can
imagine many good uses, including buying carbon
offsets~\cite{CarbonOFfsetReport}, supporting ``green'' computing
research\bcp{can we mention some specifics?}, and defraying the costs of
virtualizing conferences (livestreaming, etc.).  \bcp{Expand this paragraph
  a bit.}

@@

\bcp{I wish we could put a paragraph here about the long-term picture and
  the need to rethink scientific exchange and ACM's business model.  That
  will please our grumpy reviewer, and I think it's actually a point worth
  making.}

The climate crisis is too important to ignore and too urgent to leave for
world leaders to address at their own pace: Organizations at every scale
must confront their own contributions, raise awareness among their members,
and begin establishing new ways of doing business in the lower-carbon future
that is coming.  ACM should lead the way!
